%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} % For hyperlinks
\usepackage{fontspec}
\setmainfont{Arial}
\hypersetup{
    colorlinks=true,  % Enable colored links
    linkcolor=black,  % Color of internal links
    citecolor=black,  % Color of citation links
    urlcolor=blue     % Color of external links
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{NGUYEN NHAT TAN} % Your name
\address{District 7, Ho Chi Minh City} % Your address
\address{(+84) 858.111.879 \\ nguyennhattan.work@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EXECUTIVE SUMMARY & CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Executive Summary \& Career Objective}
As a Full Stack Developer with 4 years of experience, I have a strong foundation in ReactJS, TypeScript, NextJS, and Java Spring Boot. My goal is to contribute to a dynamic company's success as a Full Stack Developer, continuously learning and improving to deliver effective solutions. I stay up-to-date with the latest software development technologies and best practices, striving to become a valuable asset to any team I join.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
{\bf Middle Full Stack Developer, FPT Information System (FPT IS)} \hfill {\em 09/2025 – Present}
\\ \textbf{Project: Data Platform}
\\ \textbf{Team Size:} 8 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Designed, developed, and maintained backend services using Java Spring Boot.
    \item Implemented data access layers with Spring Data JPA and optimized performance using native SQL queries.
    \item Developed real-time data communication features using WebSocket and Server-Sent Events (SSE).
    \item Applied Spring Validation to ensure data integrity and request correctness.
    \item Secured APIs and system access using Spring Security.
    \item Built event-driven data pipelines using Apache Kafka for asynchronous processing.
    \item Implemented search and analytics features with Elasticsearch.
    \item Set up centralized logging and monitoring using ELK Stack (Elasticsearch, Logstash, Kibana) along with Filebeat and Metricbeat.
    \item Worked with both relational and NoSQL databases including PostgreSQL and MongoDB.
    \item Developed user interfaces using ReactJS and Material UI (MUI).
    \item Participated in system design discussions, code reviews, and cross-team collaboration.
\end{itemize}

\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{Backend:} Java Spring Boot, Spring Data JPA, Spring Validation, Spring Security, WebSocket, Server-Sent Events, Kafka
    \item \textbf{Search \& Monitoring:} Elasticsearch, Logstash, Filebeat, Metricbeat, Kibana
    \item \textbf{Frontend:} ReactJS, Material UI (MUI)
    \item \textbf{Database:} PostgreSQL, MongoDB
    \item \textbf{Big Data:} Hadoop
\end{itemize}
{\bf Middle Full Stack Developer, FPT Information System (FPT IS)} \hfill {\em 04/2025 – 09/2025}
\\ \textbf{Project: Big Data System}
\\ \textbf{Team Size:} 10 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Developed and maintained scalable Spring Boot microservices architecture.
    \item Utilized OpenAI API for analytics, forecasting, and statistical insights based on data from Excel files and multiple databases (PostgreSQL, MongoDB, MySQL, SQL Server, Oracle).
    \item Integrated Redis for caching and Elasticsearch for advanced search functionalities.
    \item Set up centralized logging infrastructure by collecting application logs with Logstash.
    \item Designed and deployed Kafka-based messaging systems for real-time event processing.
    \item Secured applications with Spring Security.
    \item Built responsive UIs with ReactJS and TypeScript.
    \item Containerized services using Docker for local and production environments.
    \item Collaborated using Jira for agile planning and sprint tracking.
\end{itemize}
\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{Backend:} Spring MVC, Spring Web Flux, Spring Security, Spring Data JPA, Kafka, Redis, Elasticsearch, Logstash, Hibernate(Native SQL queries)
    \item \textbf{Frontend:} ReactJS, TypeScript
    \item \textbf{AI:} OpenAI API
    \item \textbf{Database:} PostgreSQL, MongoDB
    \item \textbf{Deployment:} Docker, GitLab
    \item \textbf{Project Management:} Jira
\end{itemize}
{\bf Full Stack Developer, TMA Solutions} \hfill {\em 07/2024 – 03/2025}
\\ \textbf{Project: AI Automation Test System}
\\ \textbf{Team Size:} 8 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Utilized Azure OpenAI to generate test cases and execute them in real-time.
    \item Implemented WebSocket and Event Stream technology for real-time data \& real-time logging.
    \item Developed a hierarchical structure for managing test cases.
    \item Created an agent to run test cases and view test reports.
    \item Set up a deployment pipeline.
    \item Developed and implemented an integrated video recording system to capture test case execution.
\end{itemize}
\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{React (TypeScript):} Radix for theming, CodeMirror for the code editor
    \item \textbf{Java:} Spring Security, Spring WebSocket, Spring Oauth2, Spring JPA, Spring Actuator, Spring Mail, Schedule, Spring Data Redis, Spring Doc, Fasterxml Jackson(JSON library), JGit, Lombok, Gradle
    \item \textbf{Azure OpenAI:} For test case generation
    \item \textbf{WebSocket \& Event Stream:} For real-time data \& logging 
    \item \textbf{Python:} For automation scripts
    \item \textbf{Database:} SQL Server
    \item \textbf{Docker:} Set up agents for running test cases using Cypress, Selenium (Python, CSharp) and Playwright (Python)
    \item \textbf{DevOps:} Kubernetes, Linux Scripting, CI/CD pipelines with Azure DevOps
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Vitest, Junit, Mockito, Eslint, Prettier
\end{itemize}

\vspace{0.2cm} % Add some space before the next project

{\bf Full Stack Developer, TMA Solutions} \hfill {\em 04/2023 – 06/2024}
\\ \textbf{Project: Semantic Search}
\\ \textbf{Team Size:} 15 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Contributed to the design and development of semantic search features.
    \item Collaborated with cross-functional teams to implement new search algorithms.
    \item Integrated Azure AI Search and OpenAI to enhance semantic query capabilities.
    \item Developed and optimized data crawling solutions using Python and FastAPI.
    \item Set up a deployment pipeline.
\end{itemize}
\textbf{Technologies Used:}
\begin{itemize}
    \item \textbf{React (TypeScript):} Vite, Radix, Tailwind, React Hook Form, @stomp/stompjs (WebSocket), Axios, ESLint, Prettier, ag-grid-react, Husky, ChartJS
    \item \textbf{Java:} Spring Security, Spring Oauth2, Spring JPA, Spring WebSocket, Spring Data, Spring Data Redis, Spring Actuator, Spring Mail, Lombok, Spring Session, Spring Doc, Gradle
    \item \textbf{Azure Services:} Azure AI Search, Azure OpenAI, Redis, Azure Storage Account, SQL Server
    \item \textbf{Python:} FastAPI, Scrapy (Data Crawling), Playwright, WebSocket
    \item \textbf{Docker:} Setup agents to crawl data from a specific site
    \item \textbf{DevOps:} Kubernetes, Linux Scripting, CI/CD pipelines with Azure DevOps
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Vitest, Junit, Mockito, Eslint, Prettier
\end{itemize}

\vspace{0.2cm} % Add some space before the next project

{\bf Full Stack Developer, TMA Solutions} \hfill {\em 01/2022 – 03/2023} 
\\ \textbf{Project: DHP Eventbus}
\\ \textbf{Team Size:} 6 members
\\ \textbf{Job overview and responsibilities:}
\begin{itemize}
    \item Developed new features for existing projects.
    \item Maintained and supported existing features.
    \item Implemented unit tests for developed features.
    \item Configured infrastructure for deployment.
\end{itemize}
\textbf{Technologies Used:} 
\begin{itemize}
    \item \textbf{React (TypeScript):} Vite(migrate from create-react-app), Micro Frontend, Webpack, Antd, WebSocket (stompjs), Axios, ESLint, Prettier, Husky
    \item \textbf{Java:} Spring Web, Apache Pulsar, Spring JPA, Spring Clould Vault, Fasterxml Jackson (Json library), Spring security, Spring Mail, Spring Doc, Gradle
    \item \textbf{SQL Server:} Database management and optimization
    \item \textbf{DevOps:} Azure DevOps, Kubernetes, Docker
    \item \textbf{Testing:} Jest (UI testing), Mockito \& JUnit (Backend testing), Selenium (Automation testing)
    \item \textbf{Code Quality and Analysis Tools:} Sonar, Checkstyle, Junit, Mockito, Jest, Eslint, Prettier
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
{\bf Flow Chart App} \hfill {\em 06/2023 – Present}
\\ \textbf{Technologies Used:} NextJS, Next Auth, MUI, Java Spring Boot, Tailwind, PostgreSQL, Azure DevOps, Jest
\\ \textbf{Description:} An editor for building charts and diagrams.
\\ \textbf{Repo:} \href{https://dev.azure.com/nhattan1506/Public-Project/_git/flow-chart-app}{Flow Chart App}
\\ \textbf{Website:} \href{https://tannguyen.id.vn}{tannguyen.id.vn}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
{\bf Hard Skills}
\begin{itemize}
    \item ReactJS, TypeScript, Java Spring Boot, NextJS, NodeJS
    \item Antd, Material UI, Radix, ChartJS, Highcharts, React Ag-Grid
    \item Java (Spring Boot, Spring Security, Spring Data JPA, Spring OAuth2, Schedule, Spring Data Redis, Spring Mail, Spring Actuator, Spring Cloud, Lombok, Hibernate)
    \item HTML, CSS, JavaScript (ES6+), Responsive Design
    \item OAuth2, JWT for authentication and authorization
    \item Redis, Apache Kafka, Apache Pulsar, RabbitMQ
    \item Elasticsearch, Logstash for search and logging
    \item OpenAI API, Azure OpenAI
    \item Docker, Kubernetes, GitLab CI/CD, Azure Pipeline
    \item SQL Server, PostgreSQL, MongoDB, MySQL, Oracle
    \item Design Patterns, Clean Code, Microservices Architecture
    \item Sonar, Checkstyle, Gradle, ESLint, Prettier
\end{itemize}

{\bf Soft Skills}
\begin{itemize}
    \item Teamwork
    \item Agile, Kanban
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Can Tho University} \hfill {\em 09/2018 - 09/2022} 
\\ \textbf{Major:} Information Technology \hfill { GPA: 3.42/4 }
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Achievements}
\begin{itemize}
    \item {\bf TMA Star Performers}: Recognized for outstanding contributions and performance at TMA Solutions.
\end{itemize}
\end{rSection}

\end{document}
